TUDataset: A collection of benchmark datasets for learning with graphs

### 2020-07-06 paper/main.tex

\begin{abstract}
Recently, there has been an increasing interest in (supervised) learning with graph data, especially using graph neural networks.  However, the development of meaningful benchmark datasets and standardized evaluation procedures is lagging. That is, most papers still evaluate their methods on small-scale datasets leading to high standard deviations and hard to interpret results, consequently hindering advancements in this area. To address this, we introduce the \textsc{TUDataset} for graph classification and regression. The collection consists of over 120 datasets of varying sizes from a wide range of applications. We provide Python-based data loaders, kernel, and graph neural network baseline implementations, and evaluation tools. Here, we give an overview of the datasets, standardized evaluation procedures, and provide baseline experiments. All datasets are available at \url{www.graphlearning.io}. The experiments are fully reproducible from the code available at \url{www.github.com/chrsmrrs/tudataset}.
\end{abstract}

\section{Introduction}
Graph-structured data is ubiquitous across application domains ranging from chemo- and bioinformatics~\cite{Barabasi2004,Sto+2020} to image~\cite{Sim+2017} and social network analysis~\cite{Eas+2010}. To develop successful machine learning models in these domains, we need techniques that can exploit the rich information inherent in the graph structure, as well as the feature information contained within nodes and edges. In recent years, numerous approaches have been proposed for machine learning with graphs---most notably, approaches based on \new{graph kernels}~\cite{Kri+2019} and \new{graph neural networks} (GNNs)~\cite{Sca+2009,Gil+2017}. However, most papers, even recent ones, evaluate newly proposed architectures or methods on a fixed set of small-scale benchmark datasets leading to high standard deviations and hard to interpret results. 
Moreover, non-standardized experimental setups are used, which hinders the comparison of results from different publications.

>>>>

\begin{abstract}
Recently, there has been an increasing interest in (supervised) learning with graph data, especially using graph neural networks.  However, the development of meaningful benchmark datasets and standardized evaluation procedures is lagging, consequently hindering advancements in this area. 
% That is, most papers still evaluate their methods on small-scale datasets leading to high standard deviations and hard to interpret results
To address this, we introduce the \textsc{TUDataset} for graph classification and regression. The collection consists of over 120 datasets of varying sizes from a wide range of applications. We provide Python-based data loaders, kernel, and graph neural network baseline implementations, and evaluation tools. Here, we give an overview of the datasets, standardized evaluation procedures, and provide baseline experiments. All datasets are available at \url{www.graphlearning.io}. The experiments are fully reproducible from the code available at \url{www.github.com/chrsmrrs/tudataset}.
\end{abstract}

\section{Introduction}
Graph-structured data is ubiquitous across application domains ranging from chemo- and bioinformatics~\cite{Barabasi2004,Sto+2020} to image~\cite{Sim+2017} and social network analysis~\cite{Eas+2010}. To develop successful machine learning models in these domains, we need techniques that can exploit the rich information inherent in the graph structure, as well as the feature information contained within nodes and edges. In recent years, numerous approaches have been proposed for machine learning with graphs---most notably, approaches based on \new{graph kernels}~\cite{Kri+2019} and \new{graph neural networks} (GNNs)~\cite{Sca+2009,Gil+2017}.
Therefore, authoritative experimental evaluations are becoming increasingly important. However, these are complicated by the fact that (i) graph models are non standardized leading to different versions derived from the same source, and (ii) the experimental setup is not standardized. This hinders the comparison of results from different publications.
Moreover, strong baseline methods are not used throughout the literature and the considered benchmark data sets are often too small, too easy to solve or insufficiently diverse.
